NHF1_FeatureRelativeDataGeneration

### 2023-07-28 R/NHF1_FeatureRelativeDataGeneration.Rmd
Included new mismatch types in relation data gen

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T_CC>TT` = NULL)
features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL, `hg19_mnase_all` = NULL)

>>>>

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL, `hg19_mnase_all` = NULL)
